Block bootstrap consistency\\under weak assumptions

### 2017-01-10 subs/ETr4/reply_4.tex
Add new LaTeX files for response to referees and editor

\begin{document}
\section*{\hfill Reply to referee 3\hfill}

\begin{enumerate}
\item \emph{$\pi$ or $c$? Which is it?} (page 4, lines --10 and --1)

\item \emph{``independent \underline{and} can\dots''} (Page 5 line --3)

\item \emph{Should $\Em(\cdot)$ read $\Em^*(\cdot)$ here? Similarly
    for $\Em(\cdot)$ and $\Pm(\cdot)$ on the next line.}

  \emph{Just to clarify:
    \begin{itemize}
    \item $\Em^*(\cdot)$ denotes the expectation over the $u$, holding
      sample and the $M_{ni}$ fixed?
    \item $\Em(\cdot)$ denotes the expectation over sample and
      $u_{ni}$, holding only $M_{ni}$ fixed?
    \item $\E^*(\cdot)$ denotes the expectation over $u_{ni}$ and
      $M_{ni}$, holding sample fixed?
    \end{itemize} 
    (Ditto for the probabilities.) This could all be spelt out more
    clearly.}  (Page 7. Line --6)

\item \emph{``any function $g$\dots.'' Are there no restrictions of any
    kind on $g$? If so, this deserves comment.} (Page 9)

\item \emph{I assume $\Em \Em^* = \Em$, law of iterated
    expectations. Yes?  Same on the following page.} (Page 10, equation (25))

\item \emph{``Attributed to Polya ...''. If this is worth saying, it
    is worth providing a citation.} (Page 11, line --5)

\item \emph{Having $n$ on both sides of the limit is untidy, to say
    the least. If what is meant is that the two functions of n have
    the same limit, as it appears, there must be a neater way to write
    this?} (Page 14, lines --8 and --7)

\item \emph{Since these arguments are nonnegative (they're
    probabilities), what is the purpose of enclosing them in absolute
    value bars?} (Page 15, line --5) 
\end{enumerate}

>>>>

\begin{document}
\section*{\hfill Reply to referee 4\hfill}

\emph{On page 10, I did not understand Equation (25)\dots}
